Aircraft Wildlife Collisions

### 2021-07-19 draft_final.Rmd
PDF with aircraft models wordcloud (without shape)

---
title: "Aircraft Wildlife Collisions"
author: "Alexander Flick & Vy Nguyen"
date: "21/07/2021"
output:
  html_document:
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
bibliography: references.bib  
---

@@

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass, angle=angle) +
  geom_text_wordcloud_area(
    mask = png::readPNG(source="C:/Users/Alex/Documents/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +#scale_color_continuous("Blues") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )

>>>>

---
title: "Aircraft Wildlife Collisions"
author: "Alexander Flick & Vy Nguyen"
date: "21/07/2021"
output:
  pdf_document:
    toc: true
    toc_depth: 3
  html_document:
    toc: true
    toc_depth: 3
bibliography: references.bib  
---

@@

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass, angle=angle) +
  geom_text_wordcloud_area(
    #mask = png::readPNG(source="/Users/Vy/Documents/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +#scale_color_continuous("Blues") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )
